\huge On the Origin of Shrimpoluminescence

### 2021-11-10 sonoluminescence/proposal/prop.tex
asdsad

\section{Details...}
Pistol shrimp, like the red-banded pistol shrimp shown on the cover, are capabale of generating a jet of water with high enough velocity that a cavitation bubble forms behind it. When the bubble collpases, a powerful shock-wave is produced that can kill the shrimp's prey \cite{versluis2000snapping}. If the shrimp's prey had very sensitive eyes (and also weren't dead) they might notice a flash of light is also produced through an effect referred to as ``shrimpoluminescence" in the case of the pistol shrimp \cite{lohse2001snapping}, but more generally known as \emph{sonoluminescence}.

>>>>

\section{Details...}
Pistol shrimp, like the red-banded pistol shrimp shown on the cover, are capabale of generating a jet of water with high enough velocity that a cavitation bubble forms in its wake. When the bubble collpases, a powerful shock-wave is produced that can kill the shrimp's prey \cite{versluis2000snapping}. If the shrimp's prey had very sensitive eyes (and also weren't dead) they might notice a flash of light is also produced through an effect referred to as ``shrimpoluminescence" in the case of the pistol shrimp \cite{lohse2001snapping}, but more generally known as \emph{sonoluminescence}.
